Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-11 popl24/pmf.tex
checkpoint

>>>>

\paragraph{Example \ref{example-lambda-obliv}(a) revisited} As demonstrated
by Example \ref{example-lambda-obliv} taken from \cite{darais2019language}, it is possible
to leak information probabilistically through observable dependencies
in views. We can see that the adversarial views $\vx{0}{0}$ and $\vx{0}{1}$
are both 1 in three different runs of the protocol, and in 2 out of 3
the honest secret $\sx{1}{0}$ is 1 (clearly illustrated later in
Figure \ref{fig-basic-distributions}). More precisely:
$$
(\progd(\prog_{\ref{example-lambda-obliv}(a)}))(\{\sx{1}{0} \mapsto 1 \}|\{ \vx{0}{0} \mapsto 1, \vx{0}{1} \mapsto 1 \}) = 2/3
$$ An important point illustrated by this example is that the
probability of values in views, and not just the values themselves,
can release information to the adversary.  More examples are provided
in Appendix \ref{section-exmaples}.
